---
title: "Beekeeper and Related packages"
format: html
editor: source
editor_options: 
  chunk_output_type: console
collapse: true
---

```{r}
library(DiagrammeR)
library(DiagrammeRsvg)
library(rsvg)
library(here)
```


```{r graph}
DiagrammeR::grViz("
  digraph rmarkdown {
    vector -> atomic -> character
    atomic -> numeric
    atomic -> logical
    numeric -> double
    numeric -> integer
    integer -> factor
    double  -> date
    double -> POSIXct
    vector -> list
  }
  ", height=600)
```
simple_flowchart
```
### BEEKEEPER ecosystem
```{r}
# Create a simple flow chart using grViz() -------------------------------------  
simple_flowchart <- grViz(
  "digraph {

    graph[layout = dot, rankdir = LR] # Set node direction
    node[shape = box, style = filled] # Set global node attributes 
                     
    box1[style = 'invis']

    a[label = 'anyagi \n This package to find ....', fillcolor = 'green']
    b[label = 'apisguru',  fillcolor='gold']                    
    c[label = 'httr2', fillcolor = 'gold']
    d[label = 'rapid \n Convert an API description (APID), such as one that follows the OpenAPI Specification, to an R API description object', fillcolor = 'gold']

    f[label = 'nectar \n An opinionated framework for use within api-wrapping R packages', fillcolor = 'white']

  g[label='beekeeper \n Use beekeeper to create and maintain R packages that wrap APIs.']

h[label = 'mockplumber' ]

    d -> c
  }"
  )

simple_flowchart
```
```{r}
simple_flowchart %>% 
  export_svg %>%
  charToRaw %>%
  rsvg_svg(here("dv-using_diagrammer-simple_grvis.svg"))
```
